Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-04 submission.tex
More refs to intro

\section{Introduction}
\label{sec:intro}
PoS tagging is an important preprocessing step for many NLP tasks,
such as dependency parsing \cite{Niv:Hal:Kub:07,Haj:Cia:Joh:09}, named
entity recognition and sentiment analysis
\cite{Wil:Wie:Hof:09}. Whereas much effort has gone into the
development of PoS-taggers, to the effect that this task is often
considered more or less a solved task, considerably less effort has
been devoted to the empirical evaluation of the PoS tag sets
themselves. Error analysis of PoS-taggers indicate that, whereas
tagger improvement though means of learning algorithm or feature
engineering seems to have reached something of a plateau, linguistic
assessment of the distinctions made by the PoS tag set may be a venue
worth investigating further \cite{Man:11}.  Clearly, the utility of a
PoS tag set is tightly coupled with the the downstream task for which
it is performed. Even so, PoS tag sets are usually employed in a ``one
size fits all'' fashion, regardless of the requirements posed by the
task which makes use of this information.

It is well known that syntactic parsing often benefits from quite
fine-grained morphological distinctions \cite{Zha:Niv:11}. Morphology
interacts with syntax though phenomena such as agreement and case
marking and incorporating information on morphological properties of
words can therefore often improved parsing performance. However, in a
realistic setting where the aim is to automatically parse raw text,
the generation of morphological information will often require a
separate step of morphological analysis that can be quite costly.

>>>>

\section{Introduction}
\label{sec:intro}
PoS tagging is an important preprocessing step for many NLP tasks,
such as dependency parsing \cite{Niv:Hal:Kub:07,Haj:Cia:Joh:09}, named
entity recognition \cite{Tjo:DeM:03} and sentiment analysis
\cite{Wil:Wie:Hof:09}. Whereas much effort has gone into the
development of PoS-taggers, to the effect that this task is often
considered more or less a solved task, considerably less effort has
been devoted to the empirical evaluation of the PoS tag sets
themselves. Error analysis of PoS-taggers indicate that, whereas
tagger improvement though means of learning algorithm or feature
engineering seems to have reached something of a plateau, linguistic
assessment of the distinctions made by the PoS tag set may be a venue
worth investigating further \cite{Man:11}.  Clearly, the utility of a
PoS tag set is tightly coupled with the the downstream task for which
it is performed. Even so, PoS tag sets are usually employed in a ``one
size fits all'' fashion, regardless of the requirements posed by the
task which makes use of this information.

It is well known that syntactic parsing often benefits from quite
fine-grained morphological distinctions
\cite{Zha:Niv:11,See:Kuh:13}. Morphology interacts with syntax though
phenomena such as agreement and case marking and incorporating
information on morphological properties of words can therefore often
improved parsing performance. However, in a realistic setting where
the aim is to automatically parse raw text, the generation of
morphological information will often require a separate step of
morphological analysis that can be quite costly.
